We kind of need a title

### 2020-04-07 paper.tex
Sections 2 and 4

	\section{Basics of Artificial Intelligence}\label{introtoai}
		Artificial Intelligence (AI) in its basic form is a computer program that takes in an input or inputs and produces an output.  An example would be if a program took in how many hours it had been since someone washed their hands and determined whether they were due for washing their hands or not  The AI would have a threshold that would trigger a recommendation to shower.  For the purpose of this example, we will set it at two hours.  If it had been half an hour since someone washed their hands, it would not tell them to wash their hands, but if it had been five hours since they washed their hands, the AI would recommend washing their hands.  However, we know time is not the only factor in whether someone should wash their hands.  To better improve this theoretical AI, a second input could be added such as whether the person is about to touch or consume food.  In general, people should wash their hands if they are about touch or consume food.  The updated logic in the AI is that it will recommend a washing hands if the time since the last time someone washed their hands is greater than two hours or if they are about to touch or consume food. Only one condition has to be true to recommend a washing hands, but both could be true.  The more inputs or parameters that the AI takes in the better it will get a giving a correct output as long the researcher determined the correct thresholds for the AI.

		Eventually as the AI gets more complex, two problems present themselves.  First, not all problems that an AI tries to solve has a simple linear relation between their inputs and the output.  Second, the researcher may not know the exact relation between the inputs and the output.  This is where a subset of AI called Machine Learning (ML) comes into play.  A common type of  ML is called a Neural Network (NN) which more or less simulates a brain to a far lesser extent.  The way the brain works is it has many neurons that are connected together by axons and synapses. Axons are used to transport the electrical signals for the neurons. Synapses receive the signals at the end of the axons. Each synapse has a strength that determines how important the signal matters whether from another neuron or an input from the body. A neuron can have multiple inputs. The neuron sums all the signals with some mattering more than the others based on their synaptic strength. Once the neuron reaches a certain sum, it fires sending signals to other neurons or the body. The synaptic strengths can be changed over time based on whether the response generated by the neurons was correct for whatever situation. Over time, the synaptic strengths for a neuron are optimized to provide a correct response most of the time. Neural Networks work in a similar way. Each NN has nodes and weights. Nodes are like the neurons in the brain and weights are like the synaptic strength. The most basic NN has two layers. A layer of input nodes that takes the inputs in and passes them onto the next layer, the output layer. The hidden layer takes in the input, multiplies them by their weights, and sums them. An activation function maps the sum of the adjusted inputs to the desired output. The way the NN is trained through using data with known inputs and outputs. An algorithm known as error backpropagation is used to adjust the weights. In simple terms, it compares the output using the current weights, compares it to the desired output, and adjusts the weights until there is a little to no error. The example of washing hands can also be modeled with a NN. It would have two input nodes. One would take in the number of hours since someone had washed their hands and the other would take in whether someone was about to touch or consume food. The input nodes send the inputs to the output node where the inputs would be multiplied by their weights and summed. At first the weights would be randomly assigned or assigned to an estimate based off of previous knowledge of the researcher. An activation function would then be used to turn the sum into a yes or no of whether someone should wash their hands. Training data with known inputs and outputs would be used with error back propagation to adjust the weights until the error was eliminated. More inputs can also be added to improve the NN, but the real power of NN comes by adding a layer or layers between the input and output layers. Nodes can also be added to these layers. The more nodes the better. Once there is more than one layer, the connections between the nodes of separate layers can be chosen. The nodes of the previous layer do not have to connect to all the nodes of the next layer. More layers, nodes, and connections will make the NN better, but as the complexity increases, the time that it takes for the NN to produce an output increases. At a certain point of adding layers, nodes, and connections, the improvement of the success rate will be marginal in comparison with increase in time to run the NN. Neural Networks are used to model nonlinear problems linearly which can be very useful in the medical field.

		% Machine learning (ML).

		% We really need to work hard to make it clear that we are discussing primarily ML models and not procedural AI. I've basically replaced AI with ML model in almost every part I've been writing below.

		% We need to detail the difference between supervised and unsupervised training.

@@

		In their book Principles of Biomedical Ethics, Beauchamp and Childress outline four principles: autonomy, beneficence, nonmaleficence, and justice. Each principle is used to help medical profesional make decisions on treating patients.

		The first principle autonomy refers to the ability to decide for oneself free from control of others and with sufficient level of understanding as to provide for meaningful choice. Also, the person deciding should have capacity to make the choice. Next, beneficence is the principle of weighing the risks against benefits in order to get the best result. This applies to not only the patient, but it also applies to society in general. The benefits to society should be considered when weighing the risks. Nonmaleficence can be summed up with primum non nocere, first do no harm. A medical professional should do no harm. Finally, justice addresses the question of who receives healthcare resources as they are in sarces supply.

	\section{Expectations of Medical AI}
		% This section will go into how nurses and patients view medical AI, as well as how they expect it to function. This will make heavy use of gathered survey data and highlight both differences between the two groups, and just general areas that could cause some concern if they are not kept in mind while developing medical applications of machine learning.

		A number of surveys summarized by Vayena \emph{et al.} show a clear divide between popular and professional opinion on medical ML: "63\% of the adult population [of the United Kingdom] is uncomfortable with allowing personal data to be used to improve healthcare and is unfavorable to artificial intelligence (AI) systems replacing doctors and nurses in tasks they usually perform." However, drawing from a German survey, they express that a large portion of medical students believe wholeheartedly that machine learning will improve medicine. Though they are not eager enough to embrace it with little caution, expressing that they are "skeptical that it will establish conclusive diagnoses." This opinion is roughly mirrored by another United States survey cited by the authors of the article.\cite{Vayena2018}

		We chose to conduct our own survey of nursing students to gather further opinions on the subject. As a frequently understaffed and overworked profession\cite{doi:10.1111/j.1365-2648.2009.05082.x}, we believe that among healthcare professionals they stand to gain the most from advances in medical ML. Our survey ran from... \textbf{(Fill this in later! --Max)}

@@

			What it means to pass the premarket review can also change based on political and outside influences. Depending on what ideology controls the government can drastically change how hard or easy it is to pass the premarket review. One side is more of the spectrum is more inclined to push for a less restricted market. The other side is going to push for tighter regulations. In either case, there needs to be a balance between free market and regulation. Without enough free market, a few companies could control the majority of medical AI’s. On the flip side with no regulation, patients’ well-being comes to be at risk. The balance needs to be such that there is competition, but without risk to the patients. Lobbyists can also affect what goes into passing the premarket review. Initially, it will be companies sending these lobbyists likely to push for less regulations. However, eventually some type of activist group will show up to lobby for tighter regulations if medical AI’s have become risky.

@@

			There are still problems and things to consider. It is hard to define what is “good enough” for these unit tests. In testing, edge cases are difficult to identify in something as complex as a medical AI. The performance of the AI might go up for what the unit tests are checking for, but could get incrementally worse for sometiming not check. Another thing to consider is political influence. Depending on the politics at the time, what is “good enough” could be lowered to the point of risking patients’ health.

>>>>

	\section{Basics of Artificial Intelligence}\label{introtoai}

		Artificial Intelligence (AI) in its basic form is a computer program that takes in an input or inputs and produces an output. An example would be if a program took in how many hours it had been since someone washed their hands and determined whether they were due for washing their hands or not The AI would have a threshold that would trigger a recommendation to shower. For the purpose of this example, we will set it at two hours. If it had been half an hour since someone washed their hands, it would not tell them to wash their hands, but if it had been five hours since they washed their hands, the AI would recommend washing their hands. However, we know time is not the only factor in whether someone should wash their hands. To better improve this theoretical AI, a second input could be added such as whether the person is about to touch or consume food. In general, people should wash their hands if they are about to touch or consume food. The updated logic in the AI is that it will recommend washing hands if the time since the last time someone washed their hands is greater than two hours or if they are about to touch or consume food. Only one condition has to be true to recommend a washing hands, but both could be true. The more inputs or parameters that the AI takes in, the better it will get at giving a correct output as long as the researcher determines the correct thresholds for the AI.

		Eventually as the AI gets more complex, two problems present themselves. First, not all problems that an AI tries to solve has a simple linear relation between their inputs and the output. Second, the researcher may not know the exact relation between the inputs and the output. This is where a subset of AI called Machine Learning (ML) comes into play. A common type of ML is called a Neural Network (NN) which more or less simulates a brain to a far lesser extent. The way the brain works is it has many neurons that are connected together by axons and synapses. Axons are used to transport the electrical signals for the neurons. Synapses receive the signals at the end of the axons. Each synapse has a strength that determines how important the signal matters whether from another neuron or an input from the body. A neuron can have multiple inputs. The neuron sums all the signals with some mattering more than the others based on their synaptic strength. Once the neuron reaches a certain sum, it fires sending signals to other neurons or the body. The synaptic strengths can be changed over time based on whether the response generated by the neurons was correct for whatever situation. Over time, the synaptic strengths for a neuron are optimized to provide a correct response most of the time. Neural Networks work in a similar way. Each NN has nodes and weights. Nodes are like the neurons in the brain and weights are like the synaptic strength. The most basic NN has two layers. A layer of input nodes that takes the inputs in and passes them onto the next layer, the output layer. The hidden layer takes in the input, multiplies them by their weights, and sums them. An activation function maps the sum of the adjusted inputs to the desired output. The way the NN is trained through using data with known inputs and outputs. An algorithm known as error backpropagation is used to adjust the weights. In simple terms, it compares the output using the current weights, compares it to the desired output, and adjusts the weights until there is a little to no error. The example of washing hands can also be modeled with a NN. It would have two input nodes. One would take in the number of hours since someone had washed their hands and the other would take in whether someone was about to touch or consume food. The input nodes send the inputs to the output node where the inputs would be multiplied by their weights and summed. At first the weights would be randomly assigned or assigned to an estimate based off of previous knowledge of the researcher. An activation function would then be used to turn the sum into a yes or no of whether someone should wash their hands. Training data with known inputs and outputs would be used with error back propagation to adjust the weights until the error was eliminated. More inputs can also be added to improve the NN, but the real power of NN comes by adding a layer or layers between the input and output layers. Nodes can also be added to these layers. The more nodes the better. Once there is more than one layer, the connections between the nodes of separate layers can be chosen. The nodes of the previous layer do not have to connect to all the nodes of the next layer. More layers, nodes, and connections will make the NN better, but as the complexity increases, the time that it takes for the NN to produce an output increases. At a certain point of adding layers, nodes, and connections, the improvement of the success rate will be marginal in comparison with increase in time to run the NN. Neural Networks are used to model nonlinear problems linearly which can be very useful in the medical field.\cite{introtoneuralnets}

		Artificial Intelligence exists on a scale between human driven data analysis and machine driven analysis. Closer to humans doing the analysis of data is the example of the procedural AI for washing hands. Researchers define the rules for washing hands that make the decision of whether someone should wash their hands. These rules are hard coded into the AI. Somewhere in the middle of this scale is the Neural Network version of the hand washing AI. An algorithm determines the relationship between the parameters and the output, but the researchers chose two parameters which they felt were important. At the far end of the machine driven side, algorithms do most of the work. A perfect example of this is image recognition. The only human input is a researcher that annotates the images with the correct response. The algorithm figures out what makes a dog image different from a cat image for example with no human intervention. The algorithms needed are often called deep learning algorithms due to the multiple layers of the Neural Networks they create. Deep learning algorithms have the power to find the connection between vast amounts of data and the proper output, helping humans understand something that would be otherwise too overwhelming. However the more control that is given to algorithms, the less you can guarantee accuracy or fairness. They more or less become blackboxes. Although there are these risks, algorithms or machine learning can vastly help when it comes to medicine.\cite{10.1001/jama.2017.18391}

		Artificial Intelligence in medicine mainly focuses around a few disease types: cancer, nervous system diseases, and cardiovascular diseases. These diseases have hit humanity the hardest which is why they are the focus of researchers today. In each of these diseases, diagnosis imaging has been the focus of research. This is where machine learning thrive, finding the connection between symptoms, data from other non-invasive tests and what life altering disease a patient may have. A great example of the use of machine learning in medicine is in early stroke detection. A movement detection device was used to monitor a patient's movements. The device would record both the normal movement of a person and the movement before a stroke started. By using machine learning, the device was able to tell when a person's movement patterns differed significantly from their normal ones. AI has the power to save many lives in the medical field, but researchers must be careful to not cause any unnecessary risks to patients and the medical professionals using an AI.\cite{Jiang230}

@@

		In their book Principles of Biomedical Ethics, Beauchamp and Childress outline four principles: autonomy, beneficence, nonmaleficence, and justice. Each principle is used to help medical professional make decisions on treating patients.

		The first principle autonomy refers to the ability to decide for oneself free from control of others and with sufficient level of understanding as to provide for meaningful choice. Also, the person deciding should have capacity to make the choice. Next, beneficence is the principle of weighing the risks against benefits in order to get the best result. This applies to not only the patient, but it also applies to society in general. The benefits to society should be considered when weighing the risks. Nonmaleficence can be summed up with \emph{primum non nocere}, first do no harm. A medical professional should do no harm. Finally, justice addresses the question of who receives healthcare resources as they are in scarce supply.

	\section{Expectations of ML in Medicine}
		% This section will go into how nurses and patients view medical AI, as well as how they expect it to function. This will make heavy use of gathered survey data and highlight both differences between the two groups, and just general areas that could cause some concern if they are not kept in mind while developing medical applications of machine learning.

		There are unrealistically high hopes for machine learning in medicine\cite{Chen2017,10.1001/jama.2017.18391}, and there are just as many unrealistic fears to compliment them\cite{bbc2016rroai}. We chose to conduct our own survey of nursing students to gather opinions on general expectations of ML in medicine, as well as hopes and concerns. As a frequently understaffed and overworked profession\cite{doi:10.1111/j.1365-2648.2009.05082.x}, we believe that among healthcare professionals they stand to gain the most from advances in medical ML, and thus would provide valuable insight. Unfortunately, due to the ongoing COVID-19 pandemic at the time of writing, we felt that it would be inappropriate to administer such a survey. We believed that it may cause undue distress for participants given the extenuating circumstances most find themselves in.

		A number of surveys summarized by Vayena \emph{et al.} show a clear divide between popular and professional opinion on medical ML: "63\% of the adult population [of the United Kingdom] is uncomfortable with allowing personal data to be used to improve healthcare and is unfavorable to artificial intelligence (AI) systems replacing doctors and nurses in tasks they usually perform." However, drawing from a German survey, they express that a large portion of medical students believe wholeheartedly that machine learning will improve medicine. Though they are not eager enough to embrace it with little caution, expressing that they are "skeptical that it will establish conclusive diagnoses."\cite{Vayena2018} This opinion is roughly mirrored by another United States survey cited by the authors of the article.\cite{PintodosSantos2019} These statistics illustrate a clear disconnect between popular and professional opinions, that warrants further discussion.

		\subsection{Popular Opinion}

			An article by Chen and Asch expresses how the popular hopes for the predictive power of machine learning in medicine vastly outstrip the realistic potential for the emerging technology. The limitations of data sources (such as electronic health records) can introduce bias\cite{Gianfrancesco2018} due to the fact that they were only ever intended to be used (in their current state) for clinical care and billing. They propose adding additional data sources such as browser history to diversify and improve predictive power. However, they are quick to add that even that makes some glaring assumptions regarding how closely the future will resemble the present. ML models will never be able to predict the date of a catastrophe---just the risk of one occurring within a given period of time. Regardless, they are still hopeful for the future of machine learning, showing greater concern for the potential backlash when the predictive power of machine learning doesn't meet these expectations.\cite{Chen2017}

			Chen and Asch, however make an assumption regarding the availability of numerous unfettered sources of user information in an era where large scale data breaches have become almost commonplace with, as reported by cnet, 5,183 data breaches within 2019 alone.\cite{cnet2019databreaches} With bills such as the General Data Protection Regulation (GDPR) bringing well deserved attention to the storage and processing of personal data, there has never been a time where people are more skeptical of what personal data is being collected and how it is being used, as well as bringing popular discomfort with new uses for collected data.\cite{Vayena2018} While this does promote the ethical handling of personal data, it may create greater pressure on researchers to identify a concrete reason for including a data stream; this has the potential to introduce bias through the choice of which data streams are available to a given ML model and which are deemed unnecessary.\cite{Gianfrancesco2018}

			These developments raise important questions: how much loss of privacy are the potential improvements to medical decision making given by machine learning worth? How much privacy is the public willing to part with regardless of the value? Though promises may be made regarding maintaining privacy through safe storage of data, it is evident that data breaches have become more a question of when rather than a question of if.

		\subsection{Professional Opinion}

			Shameer \emph{et al} express hope regarding the future of machine learning and cardiology, while acknowledging that there are a number of issues that must be overcome. Additionally, they note that machine learning is more likely to be a compliment to standard statistical analysis rather than a replacement.\cite{Shameer1156} This falls roughly in line with what is expressed in the article by Vayena \emph{et al}\cite{Vayena2018}, and the same trend can be seen in a number of articles.\cite{Shah2018,WU201868}

@@

			What it means to pass the premarket review can also change based on political and outside influences. Depending on what ideology controls the government can drastically change how hard or easy it is to pass the premarket review. One side is more of the spectrum is more inclined to push for a less restricted market. The other side is going to push for tighter regulations. In either case, there needs to be a balance between free market and regulation. Without enough free market, a few companies could control the majority of medical AI's. On the flip side with no regulation, patients' well-being comes to be at risk. The balance needs to be such that there is competition, but without risk to the patients. Lobbyists can also affect what goes into passing the premarket review. Initially, it will be companies sending these lobbyists likely to push for less regulations. However, eventually some type of activist group will show up to lobby for tighter regulations if medical AI's have become risky.

@@

			There are still problems and things to consider. It is hard to define what is "good enough" for these unit tests. In testing, edge cases are difficult to identify in something as complex as a medical AI. The performance of the AI might go up for what the unit tests are checking for, but could get incrementally worse for sometiming not check. Another thing to consider is political influence. Depending on the politics at the time, what is "good enough" could be lowered to the point of risking patients' health.
